---
title: "Introduction to Package binomial"
author: "Yi Chieh Chen"
date: "May 01 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```


### Binomial

The package `binomial` allows the user to implement functions for calculating probabilities of a Binomial random variable, other related calculations such as the probability distribution, the expected value, variance, and visualizations.


### Creating a `bin_var`

The first step is to create a *bin_var* object with the function `bin_variable(trials, prob)`, which takes in two arguments: *trials* and *prob*:

```{r}
bin_var <- bin_variable(trials = 5, prob = 0.5)
bin_var
```


### Summary statistics

We can view the different summary statistics of *bin_var* by using the function `summary(bin_var)`.

```{r}
summary(bin_var)
```

To view only the specific statistic of *bin_var* (e.g. mean, variance, mode, skewness, and kurtosis), try these functions: `bin_mean(trials, prob)`, `bin_variance(trials, prob)`, `bin_mode(trials, prob)`, `bin_skewness(trials, prob)`, `bin_kurtosis(trials, prob)`.

```{r}
bin_mean(trials = 5, prob = 0.5)
bin_variance(trials = 5, prob = 0.5)
bin_mode(trials = 5, prob = 0.5)
bin_skewness(trials = 5, prob = 0.5)
bin_kurtosis(trials = 5, prob = 0.5)
```


### Probability

Use the `bin_probability(success, trials, prob)` function to calculate the binomial probability at given variables.

```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

The `bin_choose(n, k)` function calculates "n choose k"

```{r}
bin_choose(n = 5, k = 2)
```


### Tables and Plots

Use `bin_distribution(trials, prob)` to create tables for the binomial probability distribution.

```{r}
bin_dis <- bin_distribution(trials = 5, prob = 0.5)
bin_dis
```

To visualize the probability distribution, use `plot(bin_dis)`.

```{r}
plot(bin_dis)
```

Use the function `bin_cumulative(trials, prob)` to create tables for the cumulative binomial probability distribution.

```{r}
bin_cum <- bin_cumulative(trials = 5, prob = 0.5)
bin_cum
```

Visualize the distribution using `plot(bin_cum)`.

```{r}
plot(bin_cum)
```


